Bringing the Power of eBPF to Open vSwitch

### 2018-10-26 paper.tex
comment out the table 1

This paper focuses on the OVS-eBPF and OVS-AFXDP projects.
A rough comparison of the two project is shown in Table~\ref{proj-compare}.
The remainder of this paper is organized as follows:
In Section~\ref{sec:background}, we first provide some background information
on eBPF, XDP, and AF\_XDP.  We then present the design, implementation, and
evaluation of the OVS-eBPF and OVS-AFXDP projects in Section~\ref{sec:ebpf}
and Section~\ref{sec:af_xdp} respectively. Finally,
Section~\ref{sec:conclusion} concludes the paper and discusses the future work.

\begin{table}
\centering
\scriptsize
\begin{tabular}{|c | c | c|}
\hline
 {\bf Projects} & {\bf OVS-eBPF } & {\bf OVS-AFXDP} \\ \hline\hline
  Packet Rate & Low & High \\ \hline
  Minimal Kernel Req. & 4.10 & 4.18 \\ \hline
  Driver Support Req. & No & Yes \\ \hline
  BPF Code Size & Large & Minimal \\ \hline
  Extensibility & Good & Great \\ \hline
  \end{tabular}
\caption{\footnotesize
Comparison of the OVS-eBPF project and OVS-AFXDP project.
}
\label{proj-compare}
\end{table}

\section{Background}
\label{sec:background}

@@

\subsection{Datapath and Netdev Interface}
OVS provides a userspace datapath interface (dpif) implementation, called
dpif-netdev. The dpif-netdev userspace datapath receives and transmits
packets from its userspace interface.  One major use case of dpif-netdev
is OVS-DPDK~\cite{ovsdpdk}, where the packet reception and transmission
are all conducted in DPDK's userspace
library. The dpif-netdev is designed to be agnostic to how the network
device accessing the packets, by an abstraction layer called netdev.
Therefore, packets can come from DPDK packet I/O library,
a Linux AF\_PACKET socket API, or in our case, the AF\_XDP socket interface,
as long as each mechanism implements its own netdev interface.
Once dpif-netdev receives a packet, it follows the same mechanism performing
parse, lookup the flow table, and apply actions to the packet.

>>>>

This paper focuses on the OVS-eBPF and OVS-AFXDP projects.
%A rough comparison of the two project is shown in Table~\ref{proj-compare}.
The remainder of this paper is organized as follows:
In Section~\ref{sec:background}, we first provide some background information
on eBPF, XDP, and AF\_XDP.  We then present the design, implementation, and
evaluation of the OVS-eBPF and OVS-AFXDP projects in Section~\ref{sec:ebpf}
and Section~\ref{sec:af_xdp} respectively. Finally,
Section~\ref{sec:conclusion} concludes the paper and discusses the future work.
\mycomment{
\begin{table}
\centering
\scriptsize
\begin{tabular}{|c | c | c|}
\hline
 {\bf Projects} & {\bf OVS-eBPF } & {\bf OVS-AFXDP} \\ \hline\hline
  Packet Rate & Low & High \\ \hline
  Minimal Kernel Req. & 4.10 & 4.18 \\ \hline
  Driver Support Req. & No & Yes \\ \hline
  BPF Code Size & Large & Minimal \\ \hline
  Extensibility & Good & Great \\ \hline
  \end{tabular}
\caption{\footnotesize
Comparison of the OVS-eBPF project and OVS-AFXDP project.
}
\label{proj-compare}
\end{table}
}
\section{Background}
\label{sec:background}

@@

\subsection{Datapath and Netdev Interface}
OVS provides a userspace datapath interface (dpif) implementation, called
dpif-netdev. The dpif-netdev userspace datapath receives and transmits
packets from its userspace interface.  One major use case of dpif-netdev
is OVS-DPDK, where the packet reception and transmission
are all conducted in DPDK's userspace
library. The dpif-netdev is designed to be agnostic to how the network
device accessing the packets, by an abstraction layer called netdev.
Therefore, packets can come from DPDK packet I/O library,
a Linux AF\_PACKET socket API, or in our case, the AF\_XDP socket interface,
as long as each mechanism implements its own netdev interface.
Once dpif-netdev receives a packet, it follows the same mechanism performing
parse, lookup the flow table, and apply actions to the packet.
